Um modelo de suporte distribuído para jogos MMOG em cenários com recursos computacionais limitados

### 2009-09-01 trunk/textos/PlanoDoutorado/planodoc_lugano.tex

Another hybrid architecture is that of FreeMMG \cite{cecin2004fsa}. In it, the couple are organized in a peer-to-par in every region of the virtual environment and server mediates the communication between different regions. Again, there is the problem of security: the pairs within a region controlling the simulation that occurs there, can subvert it. It made a probabilistic approach, using a randomly selected pair from another point of the environment to verify the simulation in that region. It is expected that if the couple wish there collude to subvert the game, at least the node inserted there to detect the invalid actions and report to the server. However, besides not completely guarantee security, the problem persists there may be many pairs communicating with many, which may compromise the quality of the game.

Outra arquitetura híbrida é a do FreeMMG \cite{cecin2004fsa}. Nela, os pares se organizam de maneira par-a-par em cada região do ambiente virtual e o servidor intermedia a comunicação entre diferentes regiões. Novamente, tem-se o problema da segurança: os pares dentro de uma região controlam a simulação que ocorre ali, podendo subvertê-la. É feita uma abordagem probabilística, utilizando um par selecionado aleatoriamente de outro ponto do ambiente para verificar a simulação naquela região. Espera-se que, caso os pares ali desejem entrar em conluio para subverter o jogo, pelo menos o nodo inserido ali detecte as ações inválidas e reporte ao servidor. No entanto, além de não garantir completamente segurança, persiste o problema de poder haver muitos pares se comunicando com muitos, o que pode comprometer a qualidade do jogo.

Já foram propostos alguns modelos que sugerem o uso de clientes conectados a um servidor distribuído. Em \cite{assiotis2006dam}, por exemplo, é proposta a divisão do mundo virtual em regiões menores, cada uma atribuída a um diferente nodo do sistema servidor. Os autores tratam a questão da consistência utilizando um mecanismo de travas -- a cada entidade presente no jogo é associada uma trava, que precisa ser obtida antes de algum dos servidores fazer quaisquer alterações. Além disso, tentou-se atacar o problema dos \emph{hotspots} (aglomerados de jogadores em uma área relativamente pequena do ambiente virtual) através do particionamento recursivo da área sobrecarregada, até que esta sobrecarga seja eliminada ou não houver mais servidores disponíveis. No entanto, há um limite para este reparticionamento, pois áreas muito pequenas implicam avatares migrando entre regiões com maior freqüência e, conseqüentemente, mais tráfego entre servidores.

>>>>

Another hybrid architecture is that of FreeMMG \cite{cecin2004fsa}. In it, the players are organized in a peer-to-peer manner in every region of the virtual environment and the server mediates the communication between different regions. Again, there is the problem of security: as the peers within a region control the simulation that occurs  there, they can also subvert it. The author proposes a probabilistic approach, using a randomly selected peer to verify the simulation in that region. It is expected that, if the peers in a given region try to subvert the game there, at least the randomly inserted node detect the invalid actions and report to the server. However, besides not completely guaranteeing security, the problem persists there may be many peers communicating with many, which may compromise the quality of the game.

Some models that suggest the use of clients connected to a distributed server have been proposed in the literature. In \cite{assiotis2006dam}, for example, it is proposed to divide the virtual world into smaller regions, each assigned to a different node of the server system. The authors address the consistency problem by using a lock mechanism -- each entity in the game is associated with a lock that must be obtained before any of the servers making any changes. In addition, they tried to address the problem of \emph{hotspots} (clusters of players in a relatively small area of the virtual environment) through the recursive partitioning of the overpopulated area until the overload is eliminated or there are no more servers available. However, there is a practical limit to this partitioning, for very small areas cause avatars to migrate between regions more often, which implies more network traffic between servers.

Finally, the authors of \cite{assiotis2006dam}, as well as several others with similar proposals \cite{ng2002msa, chertov:olb, lee2003sdl}, consider that the nodes are servers connected through a high speed and low latency network, what make their solutions only partially applicable in a scenario with highly dynamic and volatile resources, such as the peer-to-peer networks formed with volunteer resources. Such networks have some inherent problems: nodes with low availability and dependability, low bandwidth and low processing power compared to current dedicated MMOG servers maintained by MMOG developers.
